---
title: "House_price_prediction"
author: "Albina Cako, Colin Green, Lucy Zhang, Sean Zhang"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### **Abstract**\
  The House Pricing Prediction app is created for estimate the house price for both buyer and seller based on different factors such as total Sqft, house locations, etc. The deployment was constructed using ShinyApp. An user friendly app for both buyer and seller, with simple click of factors users will get an estimated housing price. The app can be used for individual buyers who want to know the final price of the houses they are interested or for individual sellers to know what is the best listing price. The app uses regression model for prediction, which was trained by the data set of Toronto housing price. The housing price is strongly correlated with other factors, for increasing the model accuracy decreasing errors, it is important to try different factors and combinations. This project will comprehensively validate four different models: decision tree, random forest, K nearest neighbors, and gradient boosting machine. This report will go through data analysis, modeling implementation and provide an optimistic result for housing price prediction. 
  

#### **Introduction**\




### **Data Analysis**\

```{r load packages, include=FALSE}
# load the packages
library(dplyr)
library(ggplot2)
library(readr)
